Approximate Code: A Cost-Effective Erasure Coding Framework for Tiered Video Storage in Cloud Systems

### 2019-04-22 Apcode-4-22/ApproximateCode.tex
version 4.1

\author{Chentao Wu}

\author{Xin Xie}

\author{Jie Li}

\author{Minyi Guo}

\author{Xubin He}
\affiliation{%
  \institution{}
}

\author{Yuanyuan Dong}
\author{Hao Lin}
\author{Jianfeng Zhang}
\authornotemark[1]
\email{webmaster@marysville-ohio.com}
\affiliation{%
  \institution{The Alibaba Group}
}

\begin{abstract}
Nowadays massive video data are stored in cloud storage systems, which are generated by various applications such as autonomous driving, news media, security monitoring, etc. Meanwhile, erasure coding is a popular technique in cloud storage to provide both high reliability with low monetary cost, where triple disk failure tolerant arrays (3DFTs) is a typical choice. Therefore, how to minimize the storage cost of video data in 3DFTs is challenge for cloud storage systems. Although there are several solutions like approximate storage technique for storage devices, it cannot guarantee low storage cost and high data reliability in storage systems concurrently.

@@

\begin{table}[]
\caption{The symbols used in this paper.}\label{parameter}
\centering\small
\begin{tabular}{|p{1cm}<{\centering}|p{6.5cm}|}
\hline \hline
Symbols & \multicolumn{1}{c|}{Description} \\ \hline
$k$ & the number of data nodes in a local stripe \\ \hline
$r$ & the number of local parity nodes in a local stripe \\ \hline
$n$ & the number of all data and parity nodes in a local stripe ($n=k+r$) \\ \hline
$h$ & the number of local stripes to construct a global stripe \\ \hline
$g$ & the number of global parity nodes \\ \hline
$N$ & total number of all nodes ($N=(k+r)h+g$) \\ \hline
$E_{i,j}$ & element at the $i$-th row and $j$-th column \\ \hline
$D_i$ & data nodes \\ \hline
$P_{I}$ & the mathematical expectation of important data being recoverable under faults that exceed fault tolerance \\ \hline
$P_{U}$ & the mathematical expectation of unimportant data being recoverable under faults that exceed fault tolerance \\ \hline
LP & local parity nodes \\ \hline
GP & global parity nodes \\ \hline
ID & important data in a video file \\ \hline
UD & unimportant data in a video file \\ \hline
\end{tabular}
\end{table}

@@

In deep learning methods, optical changes between the frames are trained in a supervised setup mapping two frames to their ground truth optical flow. Among all these, a multi-scale network\cite{van2017frame} based on recent advances in spatial transformers and composite perceptual losses has so far produced the new state-of-the-art results in terms of PSNR, and so has a context-aware Synthesis approach\cite{niklaus2018context} in terms of middlebury benchmark.

@@

\begin{figure}[!ht]
\centering
\subfigure[\textbf{STAR Code:} Horizontal parity coding (e.g., $E_{0,5} = E_{0,0} \oplus E_{0,1} \oplus E_{0,2} \oplus E_{0,3} \oplus E_{0,4}$).]{
\includegraphics[width=0.42\linewidth]{photo/star-hori.pdf}\label{fig-star-1}
}
\hspace{5pt}
\subfigure[\textbf{TIP Code:} Horizontal parity coding (e.g., $E_{0,7} = E_{0,0} \oplus E_{0,2} \oplus E_{0,3} \oplus E_{0,4} \oplus E_{0,5}$).]{
\includegraphics[height=2.5cm]{photo/tip-hori.pdf}\label{fig-tip-1}
}

\subfigure[\textbf{STAR Code:} Diagonal parity coding (e.g., $S_1 = E_{3,1} \oplus E_{2,2} \oplus E_{1,3} \oplus E_{0,4}$ and $E_{0,6} = E_{0,0} \oplus E_{3,2} \oplus E_{2,3} \oplus E_{1,4} \oplus S_1$).]{
\includegraphics[width=0.42\linewidth]{photo/star-diag.pdf}\label{fig-star-2}
}
\hspace{5pt}
\subfigure[\textbf{TIP Code:} Diagonal parity coding (e.g., $E_{0,1} = E_{0,0} \oplus E_{5,2} \oplus E_{4,3} \oplus E_{2,5} \oplus E_{1,6}$ ).]{
\includegraphics[height=2.5cm]{photo/tip-diag.pdf}\label{fig-tip-2}
}

\subfigure[\textbf{STAR Code:} Anti-diagonal parity coding (e.g., $S_2 = E_{0,1} \oplus E_{1,2} \oplus E_{2,3} \oplus E_{3,4}$ and $E_{0,7} = E_{0,0} \oplus E_{1,1} \oplus E_{2,2} \oplus E_{3,3} \oplus S_2$).]{
\includegraphics[width=0.42\linewidth]{photo/star-anti.pdf}\label{fig-star-3}
}
\hspace{5pt}
\subfigure[\textbf{TIP Code:} Anti-diagonal parity coding (e.g., $E_{0,6} = E_{0,0} \oplus E_{1,1} \oplus E_{2,2} \oplus E_{4,4} \oplus E_{5,5}$).]{
\includegraphics[height=2.5cm]{photo/tip-anti.pdf}\label{fig-tip-3}
}
\caption{Encoding of STAR (subfigure (a),(c) and (e)) and TIP (subfigure (b),(d) and (f)) code ($p = 5$). Each column represents a node, each block represents an element, and parity chains are represented by elements with same shape.}
\label{fig-star-tip}
\end{figure}

@@

%从这里开始简单讲解几种RAID-6或三盘容错阵列的纠删码，如RS，EVENODD，RDP，STAR，LRC, H-Code，TIP-Code等，并且用编码图来说明（主要是实验中用到的几种编码）。

@@

\subsubsection{\textcolor{red}{Metrics and Methods for Frame Recovery: }}
we performed the experiment of video frame recovery with the frame interpolation technique. The dataset we used is a collection of 60fps videos from \textbf{YouTube-8m} \cite{youtube8m}. We simulated a 1\% data loss\footnote{In a distributed system, a single video can be stored in dozens or even hundreds of nodes. We assume that its important data is recovered, while the loss of unimportant data accounts for 1\% of the total video size.} on the less important video frames and successfully recovered the lost ones, although the recovered frames have some discrepancies with the original data. The average quality of the recovered pictures is commonly above 35dB in terms of PSNR (Peak Signal to Noise Ratio).

>>>>

\author{Chentao Wu}
\author{Xin Xie}
\author{Jie Li}
\author{Minyi Guo}
\affiliation{
  \institution{Shanghai Jiao Tong University}
}

\author{Hao Lin}
\author{Jianfeng Zhang}
\authornotemark[1]
\affiliation{%
  \institution{The Alibaba Group}
}

\begin{abstract}
Nowadays massive video data is stored in cloud storage systems, which is generated by various applications such as autonomous driving, news media, security monitoring, etc. Meanwhile, erasure coding is a popular technique in cloud storage to provide both high reliability with low monetary cost, where triple disk failure tolerant arrays (3DFTs) is a typical choice. Therefore, how to minimize the storage cost of video data in 3DFTs is challenge for cloud storage systems. Although there are several solutions like approximate storage technique for storage devices, it cannot guarantee low storage cost and high data reliability in storage systems concurrently.

@@

\begin{table}[]
\caption{The symbols used in this paper.}\label{parameter}
\centering\small
\begin{tabular}{|p{1cm}<{\centering}|p{6.5cm}|}
\hline
Symbols & \multicolumn{1}{c|}{Description} \\ \hline \hline
$k$ & the number of data nodes in a local stripe \\ \hline
$r$ & the number of local parity nodes in a local stripe \\ \hline
$n$ & the number of all data and parity nodes in a local stripe ($n=k+r$) \\ \hline
$h$ & the number of local stripes to construct a global stripe \\ \hline
$g$ & the number of global parity nodes \\ \hline
$N$ & total number of all nodes ($N=(k+r)h+g$) \\ \hline
$E_{i,j}$ & element at the $i$-th row and $j$-th column \\ \hline
$D_i$ & data nodes \\ \hline
$P_{I}$ & the mathematical expectation of important data being recoverable under faults that exceed fault tolerance \\ \hline
$P_{U}$ & the mathematical expectation of unimportant data being recoverable under faults that exceed fault tolerance \\ \hline
LP & local parity nodes \\ \hline
GP & global parity nodes \\ \hline
ID & important data in a video file \\ \hline
UD & unimportant data in a video file \\ \hline
\end{tabular}
\end{table}

@@

In deep learning methods, optical changes between the frames are trained in a supervised setup mapping two frames to their ground truth optical flow. Among all these, a multi-scale network\cite{van2017frame} based on recent advances in spatial transformers and composite perceptual losses has so far produced the new state-of-the-art results in terms of Peak Signal to Noise Ratio (PSNR), and so has a context-aware Synthesis approach\cite{niklaus2018context} in terms of Middlebury benchmark.

@@

\begin{figure}[!ht]
\centering
\subfigure[\textbf{STAR Code:} Horizontal parity coding (e.g., $E_{0,5} = E_{0,0} \oplus E_{0,1} \oplus E_{0,2} \oplus E_{0,3} \oplus E_{0,4}$).]{
\includegraphics[width=0.42\linewidth]{photo/star-hori.pdf}\label{fig-star-1}
}
\hspace{5pt}
\subfigure[\textbf{STAR Code:} Diagonal parity coding (e.g., $S_1 = E_{3,1} \oplus E_{2,2} \oplus E_{1,3} \oplus E_{0,4}$ and $E_{0,6} = E_{0,0} \oplus E_{3,2} \oplus E_{2,3} \oplus E_{1,4} \oplus S_1$).]{
\includegraphics[width=0.42\linewidth]{photo/star-diag.pdf}\label{fig-star-2}
}

\subfigure[\textbf{STAR Code:} Anti-diagonal parity coding (e.g., $S_2 = E_{0,1} \oplus E_{1,2} \oplus E_{2,3} \oplus E_{3,4}$ and $E_{0,7} = E_{0,0} \oplus E_{1,1} \oplus E_{2,2} \oplus E_{3,3} \oplus S_2$).]{
\includegraphics[width=0.42\linewidth]{photo/star-anti.pdf}\label{fig-star-3}
}
\hspace{5pt}
\subfigure[\textbf{TIP Code:} Horizontal parity coding (e.g., $E_{0,7} = E_{0,0} \oplus E_{0,2} \oplus E_{0,3} \oplus E_{0,4} \oplus E_{0,5}$).]{
\includegraphics[height=2.5cm]{photo/tip-hori.pdf}\label{fig-tip-1}
}

\subfigure[\textbf{TIP Code:} Diagonal parity coding (e.g., $E_{0,1} = E_{0,0} \oplus E_{5,2} \oplus E_{4,3} \oplus E_{2,5} \oplus E_{1,6}$ ).]{
\includegraphics[height=2.5cm]{photo/tip-diag.pdf}\label{fig-tip-2}
}
\hspace{5pt}
\subfigure[\textbf{TIP Code:} Anti-diagonal parity coding (e.g., $E_{0,6} = E_{0,0} \oplus E_{1,1} \oplus E_{2,2} \oplus E_{4,4} \oplus E_{5,5}$).]{
\includegraphics[height=2.5cm]{photo/tip-anti.pdf}\label{fig-tip-3}
}
\caption{Encoding of STAR (Figure \ref{fig-star-1}, \ref{fig-star-2} and \ref{fig-star-3}) and TIP (Figure \ref{fig-tip-1}, \ref{fig-tip-2} and \ref{fig-tip-3}) code ($p = 5$). Each column represents a node, each block represents an element, and parity chains are represented by elements with same shape.}
\label{fig-star-tip}
\end{figure}

@@

@@

\subsubsection{\textcolor{red}{Metrics and Methods for Frame Recovery: }}
we performed the experiment of video frame recovery with the frame interpolation technique. The dataset we used is a collection of 60fps videos from \textbf{YouTube-8m} \cite{youtube8m}. We simulated a 1\% data loss\footnote{In a distributed system, a single video can be stored in dozens or even hundreds of nodes. We assume that its important data is recovered, while the loss of unimportant data accounts for 1\% of the total video size.} on the less important video frames and successfully recovered the lost ones, although the recovered frames have some discrepancies with the original data. The average quality of the recovered pictures is commonly above 35dB in terms of Peak Signal to Noise Ratio PSNR .

### 2019-04-22 ApproximateCode.tex
version 4.1

%
% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
% Please copy and paste the code instead of the example below.
%
\keywords{Erasure Codes, Approximate Storage, Multimedia, Cloud Storage}

\maketitle

@@

\begin{figure*}[ht!]
\centering
\includegraphics[width=\linewidth]{photo/Framework-v2.pdf}
\caption{The framework of Approximate Code}
\label{fig-framework}
\end{figure*}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{photo/AP-5214-v2.pdf}
\caption{The construction and the encoding process of APPR.STAR ($5,2,1,4$,Uneven), which can be divided into STAR (encode important data) and EVENODD (encode unimportant data).}
\label{fig-ap-5214}
\end{figure}

\iffalse
\begin{figure}[ht]
\includegraphics[width =0.8\linewidth]{photo/EVENODD-STAR-v2.pdf}
\caption{Encoding process of APPR.STAR($5,2,1,4$,Uneven), which can be divided into STAR (encode important data) and EVENODD (encode unimportant data).}\label{fig-star}
\end{figure}
\fi

@@

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{photo/AP-5126-v2.pdf}
\caption{The construction and the encoding process of APPR.TIP ($5,1,2,6$,Even). The node 5 and 6 in TIP code is defined as the global parity nodes in this case.}
\label{fig-ap-TIP}
\end{figure}

We then intorduce the generation of APPR.TIP($5,1,2,6$,Even).

>>>>

\keywords{Erasure Codes, Approximate Storage, Multimedia, Cloud Storage}
\maketitle

@@

\begin{figure*}[ht!]
\centering
\includegraphics[width=\linewidth]{photo/Framework-v3.pdf}
\caption{The framework of Approximate Code}
\label{fig-framework}
\end{figure*}

@@

\begin{figure}[ht]
\centering
\subfigure[Structure selection of APPR.STAR Code]{
    \label{fig-ap-tip-str}
    \includegraphics[width = 0.5\linewidth]{photo/APPR-STAR-STR.pdf}
}

\subfigure[Generation of local parities]{
    \label{fig-ap-tip-lP}
    \includegraphics[width = 0.59\linewidth]{photo/APPR-STAR-LO.pdf}
}
\subfigure[Generation of global parities]{
    \label{fig-ap-tip-GP}
    \includegraphics[width = 0.35\linewidth]{photo/APPR-STAR-GL.pdf}
}
\caption{The construction and the encoding process of APPR.STAR ($5,2,1,4$,Uneven), which can be divided into STAR (encode important data) and EVENODD (encode unimportant data).}
\label{fig-ap-5214}
\end{figure}

@@

\begin{figure}[ht]
\centering
\subfigure[Structure selection of APPR.TIP Code]{
    \label{fig-ap-tip-str}
    \includegraphics[width = 0.45\linewidth]{photo/APPR-TIP-STR.pdf}
}
\hspace{2pt}
\subfigure[Generation of local parities]{
    \label{fig-ap-tip-lP}
    \includegraphics[width = 0.3\linewidth]{photo/APPR-TIP-LO.pdf}
}

\subfigure[Generation of global parities]{
    \label{fig-ap-tip-GP}
    \includegraphics[width = 0.75\linewidth]{photo/APPR-TIP-GL.pdf}
}
\caption{The construction and the encoding process of APPR.TIP ($5,1,2,6$,Even). The node 5 and 6 in TIP code is defined as the global parity nodes in this case.}
\label{fig-ap-TIP}
\end{figure}

We then introduce the generation of APPR.TIP($5,1,2,6$,Even).
